### 2022-01-10 input/experiments.tex
experiment europe

>>>>

\begin{figure*}
  \subfloat[PartA][\label{fig:europe-ases}An edge infrastructure
    comprising 40 interconnected autonomous systems spanning across
    Europe~\cite{knight2011internet}.]{
    \includegraphics[width=\FIGSCALE\columnwidth]{img/europe-ases.pdf}
  } \subfloat[PartB][\label{fig:xascast}
    \TODO{Experiment with ascast against xascast? with different cache
      size}]{
    \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/europe_as_vs_xas.eps}
  }
  \caption{\TODO{Experiment measuring something on such a trace.} \TODO{Worst case when using as-cast}}
\end{figure*}
